### 2020-02-20 source/cadabra/geodesic-ivp.tex
Corrected typos on free indices in eqtns. 11.19*
The LaTeX source for eqtns. 11.19* (geodesic-ivp results) had incorrect free indices on the left hand side. The indices were written by hand (not by Cadabra). The Cadabra code/results are unchanged.
Corrected +/- sign error on s^2, s^3 etc.  terms in eqs. 11.19a-d
I had forgotten to take account of the minus sign in eq. 3.1 when constructing the solution to the geodesic IVP. This correction has no effect on any other results.

   sterm21 = cdblib.get ('genGamma01','genGamma.json')
   sterm22 = cdblib.get ('genGamma02','genGamma.json')
   sterm23 = cdblib.get ('genGamma03','genGamma.json')
   sterm24 = cdblib.get ('genGamma04','genGamma.json')

   sterm31 = cdblib.get ('genGamma11','genGamma.json')
   sterm32 = cdblib.get ('genGamma12','genGamma.json')
   sterm33 = cdblib.get ('genGamma13','genGamma.json')

   sterm41 = cdblib.get ('genGamma21','genGamma.json')
   sterm42 = cdblib.get ('genGamma22','genGamma.json')

   sterm51 = cdblib.get ('genGamma31','genGamma.json')

@@

\begin{align*}
   x^{d}(s) = x^{d}
            + s {\dot{x}^d}
            + \frac{s^2}{2!} {\dot{x}^a} {\dot{x}^b} A^{d}_{ab}
            + \frac{s^3}{3!} {\dot{x}^a} {\dot{x}^b} {\dot{x}^c} A^{d}_{abc}
            + \frac{s^4}{4!} {\dot{x}^a} {\dot{x}^b} {\dot{x}^c} {\dot{x}^d} A^{d}_{abce}
            + \frac{s^5}{5!} {\dot{x}^a} {\dot{x}^b} {\dot{x}^c} {\dot{x}^d} {\dot{x}^e} A^{d}_{abcef}
            + \dotsb
\end{align*}
\begin{dgroup*}
   \begin{dmath*} 360 A^{d}_{ab} = \cdb{sterm2.002} \end{dmath*}
   \begin{dmath*} 360 A^{d}_{abc} = \cdb{sterm3.002} \end{dmath*}
   \begin{dmath*}  90 A^{d}_{abce} = \cdb{sterm4.002} \end{dmath*}
   \begin{dmath*}   3 A^{d}_{abcef} = \cdb{sterm5.002} \end{dmath*}
\end{dgroup*}

>>>>

   # change signs to account for - sign in front of the sum for x^a(s), see above preamble

   def flip_sign (obj):
       return Ex(0) - obj

   sterm21 = flip_sign (cdblib.get ('genGamma01','genGamma.json'))
   sterm22 = flip_sign (cdblib.get ('genGamma02','genGamma.json'))
   sterm23 = flip_sign (cdblib.get ('genGamma03','genGamma.json'))
   sterm24 = flip_sign (cdblib.get ('genGamma04','genGamma.json'))

   sterm31 = flip_sign (cdblib.get ('genGamma11','genGamma.json'))
   sterm32 = flip_sign (cdblib.get ('genGamma12','genGamma.json'))
   sterm33 = flip_sign (cdblib.get ('genGamma13','genGamma.json'))

   sterm41 = flip_sign (cdblib.get ('genGamma21','genGamma.json'))
   sterm42 = flip_sign (cdblib.get ('genGamma22','genGamma.json'))

   sterm51 = flip_sign (cdblib.get ('genGamma31','genGamma.json'))

@@

\begin{align*}
   x^{a}(s) = x^{a}
            + s {\dot{x}^a}
            + \frac{s^2}{2!} {\dot{x}^b} {\dot{x}^c} A^{a}_{bc}
            + \frac{s^3}{3!} {\dot{x}^b} {\dot{x}^c} {\dot{x}^d} A^{a}_{bcd}
            + \frac{s^4}{4!} {\dot{x}^b} {\dot{x}^c} {\dot{x}^d} {\dot{x}^e} A^{a}_{bcde}
            + \frac{s^5}{5!} {\dot{x}^b} {\dot{x}^c} {\dot{x}^d} {\dot{x}^e} {\dot{x}^f} A^{a}_{bcdef}
            + \dotsb
\end{align*}
\begin{dgroup*}
   \begin{dmath*} 360 A^{a}_{bc} = \cdb{sterm2.002} \end{dmath*}
   \begin{dmath*} 360 A^{a}_{bcd} = \cdb{sterm3.002} \end{dmath*}
   \begin{dmath*}  90 A^{a}_{bcde} = \cdb{sterm4.002} \end{dmath*}
   \begin{dmath*}   3 A^{a}_{bcdef} = \cdb{sterm5.002} \end{dmath*}
\end{dgroup*}
